Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-18 chi2012.tex
a  few more

Looking at overlap, we notice that, there was, overall little overlap among records; that is, except for the smallest records (which had few properties to begin with), most of the data records had more unique properties than ones that overlapped with any of the other records.  While some of these 'unique records' were primarily for internal, service-specific use (such as service-speicifc IDs) others were useful properties one would expect to find in a record that were simply not present.  Only one of the music records, Spotify, included information about the album(s) that a song was featured on.  Such omissions show us that these data APIs reflect very specifically each service provider's capabilities and internal data representations, and that integrating data such records from multiple sources would allow properties to be aggregated to form more complete representations.

>>>>

Looking at overlap, we notice overall little overlap among records; that is, except for the smallest records (which had few properties to begin with), most of the data records had more unique properties than ones that overlapped with any of the other records.  While some of these 'unique records' were primarily for internal, service-specific use (such as service-speicifc IDs) others were useful properties one would expect to find in a record that were simply not present.  Only one of the music records, Spotify, included information about the album(s) that a song was featured on.  Such omissions show us that these data APIs reflect very specifically each service provider's capabilities and internal data representations, and that integrating data such records from multiple sources would allow properties to be aggregated to form more complete representations.
